\documentclass[10pt,letterpaper]{article}

  \usepackage[T1]{fontenc} 
    \usepackage{textcomp} 
   \usepackage{mathpazo} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{plain}                                                      %%
%%%%%%%%%% EXACT 1in MARGINS %%%%%%%                                   %%
\setlength{\textwidth}{6.5in}     %%                                   %%
\setlength{\oddsidemargin}{0in}   %% (It is recommended that you       %%
\setlength{\evensidemargin}{0in}  %%  not change these parameters,     %%
\setlength{\textheight}{8.5in}    %%  at the risk of having your       %%
\setlength{\topmargin}{0in}       %%  proposal dismissed on the basis  %%
\setlength{\headheight}{0in}      %%  of incorrect formatting!!!)      %%
\setlength{\headsep}{0in}         %%                                   %%
\setlength{\footskip}{.5in}       %%                                   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                   %%
\newcommand{\required}[1]{\section*{\hfil #1\hfil}}                    %%
\renewcommand{\refname}{\hfil References Cited\hfil}                   %%
\bibliographystyle{unsrt}                                              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[square, comma, sort&compress]{natbib}

\usepackage[font=small,format=plain,labelfont=bf,up,textfont=it,up]{caption}
\def\abovecaptionskip{1mm} 
\usepackage[margin=1in]{geometry}
\usepackage{url}
\usepackage{alltt}

\usepackage{cite}
\usepackage{bigstrut}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{wrapfig}
\usepackage{hhline}
\usepackage{epsf}
\usepackage{nameref}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{wrapfig} 
\usepackage{tabularx}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage[usenames]{color}
\usepackage{colortbl}
\usepackage{tabularx}
\usepackage{wasysym}
\usepackage{pdfpages}
\def\naive{na\"{\i}ve}
\def\Naive{Na\"{\i}ve}
\def\naively{na\"{\i}vely}	% Okay, I know, this isn't French.
\def\Naively{Na\"{\i}vely}
\usepackage[compact]{titlesec}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage[table,dvipsnames]{xcolor}
\newcommand{\TODO}[1]{{\it \color{blue}\{TODO: #1\}}}

\usepackage{titlesec}

\urlstyle{same}

%list margin
\usepackage{enumitem}
\usepackage{makecell}

\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.pdf, .png, .ps}

\newboolean{hidecomments}
\setboolean{hidecomments}{true}
\ifthenelse{\boolean{hidecomments}}
{\newcommand{\nb}[2]{}}
{\newcommand{\nb}[2]{
    \fbox{\bfseries\sffamily\scriptsize#1}
    {\sf\small$\blacktriangleright$
      {#2} $\blacktriangleleft$}}}
    
\newcommand\emh[1]{\nb{EMH}{#1}}
\newcommand\myTitle{\newpage
\begin{center}
{\bf SHF:Small: Mega-Transfer: On the Value of Learning from 10,000+ Software Projects}\\
Tim Menzies (North Carolina State University)
\end{center}}

\usepackage{tikz}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
 %           \node[shape=circle,fille=.,draw,inner sep=2pt] (char) {\color{-.} \bfseries\footnotesize#1};}}

\definecolor{Gray}{gray}{0.9}
\definecolor{darkgray}{gray}{0.8}
\newcommand{\circled}[1]{\tikz[baseline=(myanchor.base)] \node[circle,fill=darkgray,inner sep=1pt] (myanchor) {\color{.}\footnotesize \textbf{#1}};}

\usepackage{bbding}
\definecolor{lgray}{gray}{0.9}

\usepackage{enumitem}
\setlist{nosep}
\usepackage{todonotes}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\newcommand{\tion}[1]{\S\ref{sec:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}

\newcommand{\tbl}[1]{Table~\ref{tbl:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}

%\newcommand{\THAT}[0]{ISOP}
\newcommand{\THAT}[0]{ISOP}
\newcommand{\THIS}[0]{\mbox{this proposal}}
% paraHead
\newcommand\paraHead[1]{\noindent\textbf{#1}}
\newcommand\head[1]{\paragraph{\underline{#1}}} 
\usepackage{titlesec}


\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
              {0pt}{0pt}{0pt}
\titlespacing{\paragraph}{0pt}{3pt}{1em}
              
\newcommand{\quart}[4]{\begin{picture}(80,4)%1
	{\color{black}\put(#3,2){\circle*{4}}\put(#1,2){\line(1,0){#2}}}\end{picture}}
\usepackage[font=small,format=plain,labelfont=bf,textfont=it]{caption}

\usepackage{xcolor}
\pagenumbering{arabic}
\usepackage{enumitem}
\setlist{nosep}


\pagenumbering{arabic} 

\usepackage{pifont} 

\begin{document}
\pagestyle{plain}
\myTitle
%\pagenumbering{arabic}
\pagestyle{empty}

\head{Overview:}
Software analytics is a workflow that distills large amounts of low-value data into small chunks of very high-value data. 
After a decade of intensive software analytics, what have we learned? While that work has generated many specific results about many specific projects,
it has failed (so far) to deliver general principles that are demonstrably useful across many projects. 
Is that good enough? Surely we can do better than that,  given the ready availability much software project and  the scalablility of automated analytics.

One possible explanation for the limited conclusions (so far) from automated analytics is  {\em how much} data we are using in the analysis. 
A typical research paper in software analytics studies less than a few dozen projects.  Such small samples can never be
representative of something as diverse as software engineering
Perhaps it is   time to stop making 
limited conclusions from tiny sets of 
software projects.


To find general conclusions in SE, we propose learning from a much larger corpus than ever used before (10,000+ projects). To that end,
we propose  innovative {\em transfer learning}
methods based on  very fast clustering and transfer learners based on very fast stream mining algorithms that use incremental hyperparameter optimizers.  With these innovations, we will explore
1500+ commercial projects maintained by our industrial colleagues at Raleigh's Research Triangle;
as well as the 10,000+ projects currently available from Github.
Using this data, we  will ask and answer the question:
\begin{center}
{\bf RQ1:} {\em Can ``mega-transfer'' learning  between 10,000+ project generate better, more insightful, models?}
\end{center}
In order to demonstrate the external validity of our methods, we will watch for new releases of the projects we are studying. When such new releases occur, we will apply our current models to those new releases. This will demonstrate the value (or otherwise) of our models on new data.


\head{Intellectual Merit:} 
This paper tests the value of ``big data'' for software engineering. Is it worthwhile collecting and reasoning about large numbers of SE projects? 
Are there general principles we can use to guide project management, software standards, education,tool development, and legislation about software? Or is software engineering some ``patchwork quilt'' of ideas and methods where it only makes sense to reason about specific, specialized, and small sets of related projects?

This is an important question.
  Data science for software engineering
cannot be called a ``science'' unless
it makes general conclusions that hold across
multiple projects. Hence,  software analytics will never become a data ``science''
unless its  conclusions hold across a large space of projects. 
Accordingly, we test if there are general models of SE that apply to a wide range of projects.  
We also  propose and comparatively evaluate  methods designed for the situation where   such general models do not exist.
 

\head{Broader Impacts:}
This proposal focuses on issues of
tremendous economic importance--  the creation of better quality software.
As a result, this work will increase America's ability for industrial and academic innovators to conduct
more scientific studies via computational means.  
 

Also, the PI teaches senior-level and graduate-level SE, and data mining classes (and in those data mining classes, all the case studies come from software engineering).  All of the technology developed in this proposal will become case study material for those subjects.   The PI will continue his established tradition of graduating  research  students  for  historically  under-represented  groups.   Also, this work will inform the curriculum of the PI's annual
   NSF-funded REU (research experience for undergraduates) work on  the ``Science of Software''
   (in  this program, places are reserved for students from traditionally under-represented areas; e.g.  economically challenged regions of the state of North Carolina) and/or students from universities lacking advanced research facilities). While some of the concepts of this grant would be too advanced for that group, some of the simpler data mining concepts would be suitable for lectures and REU projects.


\head{Keywords:} software analytics, transfer learning,  prediction
\newpage
\pagestyle{plain}

\setcounter{page}{1}
\renewcommand{\thepage} {D--\arabic{page}}
\myTitle

\input{body.tex}

\newpage
\head{Facilities, Equipment, and Other Resources:}
\input{facilities}

\newpage
\bibliographystyle{unsrt}
\bibliography{references,refs-rahul}

\end{document}
